### 2022-11-13 chapter1.tex
Moved graphical overview caption text into main text

\begin{figure}[h!]
\includegraphics[width=\textwidth]{graphical_overview.png}
\centering
\caption{\textbf{Graphical summary of homology inference pipeline.}
1) Protein sequences from annotated genomes are collected. The large, open circles represent the annotated genomes, and the small, filled circles represent the protein sequences associated with each annotation. Sequences that share homology are colored with shades of the same hue. 2) Homology searches are conducted between all query-target pairs of genomes. The lines represent a statistically significant alignment between two sequences in the genome pair. 3) The raw output from the homology searches is processed to yield best hits between pairs of sequences. 4) The network of best hits is clustered into self-consistent orthologous groups. The small, filled circles and lines represent the same sequences and best hits from the previous step. 5) Orthologous groups are grouped by their parent genes, which are represented by the two sets of clusters with warm and cool colors, respectively. 6) Representative sequences in each orthologous group are aligned. Some steps are simplified or omitted for clarity.}
\label{fig:graphical_overview}
\end{figure}

\section*{Results}
\subsection*{Pipeline overview}
% TODO: Add description of pipeline, adapting text from Figure 1 caption

>>>>

\begin{figure}[h!]
\includegraphics[width=\textwidth]{graphical_overview.png}
\centering
\caption{\textbf{Graphical overview of homology inference pipeline.}
In panels A-C, the large, open circles represent the annotated genomes, and the small, filled circles represent the protein sequences associated with each annotation. Sequences that share homology are colored with shades of the same hue. In panels D-F, the small, filled circles and lines represent the same sequences and best hits from the previous steps.}
\label{fig:graphical_overview}
\end{figure}

\section*{Results}
\subsection*{Pipeline overview}
The orthology inference pipeline is summarized in Figure \ref{fig:graphical_overview}. Overall, the approach is similar to other graph-based methods of orthology inference. First, protein sequences from annotated genomes are collected (Fig.~\ref{fig:graphical_overview}A), and homology searches are then conducted between all query-target pairs of genomes (Fig.~\ref{fig:graphical_overview}B). The raw output from these homology searches is processed to yield best hits between pairs of sequences (Fig.~\ref{fig:graphical_overview}C). Next, the network of best hits is clustered into self-consistent orthologous groups (Fig.~\ref{fig:graphical_overview}D). Since genes can have multiplied associated isoforms, we then implemented a novel second clustering step where orthologous groups are grouped by their parent genes, which are represented by the two sets of clusters with warm and cool colors, respectively (Fig.~\ref{fig:graphical_overview}E). Finally, representative sequences in each orthologous group are aligned (Fig.~\ref{fig:graphical_overview}F). In the following sections, we discuss each of these and other steps which were omitted for clarity in greater detail.
